### 2017-09-20 Graduate - Introduction to Analysis I/Assignment 3/3_Homework20170911.tex
update

\textbf{(b)}. 
According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step. Thus according to the construction of Cantor function, we have $\varphi(x) = \sum_{k}(\frac{1}{2}c_k)2^{-k}$.
\bigskip

>>>>

\textbf{(b)}. 
% According to (a), if we count the numbers starting by $0$, then $x$ is in the $c_{k}^{th}$ set in $k^{th}$ step. Thus according to the construction of Cantor function, we have $\varphi(x) = \sum_{k}(\frac{1}{2}c_k)2^{-k}$.
First, assume $x\in O$. According to the construction of Cantor function, if $x = \sum_{k} c_k3^{-k}$ is the ternary expansion of $x$, and the first $1$ in the ternary expansion is in the $n_{th}$ place, then $\varphi(x) = \frac{1}{2^n} + \sum_{k < n}\frac{1}{2}c_k 2^{-k} $.

If $x = \sum_{k}c_k3^{-k}\in C$, according to the extension of $\varphi(x)$, $\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} $. We can construct a sequence $\{t_i\} = \{\sum_{k} d_k3^{-k}\}$, s.t. $d_i = c_i, \forall i < m_{i+1} $, where $m_i $ is the position of $i_{th}~ 2~ \text{in}~ c_k $, and $d_{m_{i+1}} = 1$. Then $\{t_i\}$ is a strictly increasing sequence, and $\lim_{i\to\infty}t_{i} = x$.

Since $\varphi(x)$ is a strictly increasing function in $O$, we know that
$$
\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} \ge \varphi(t_i) = \frac{1}{2^i}+\sum_{k<i}\frac{1}{2}d_k2^{-k}.
$$ 
Thus 
$$
\varphi(x) \ge \sum_{k}\frac{1}{2}c_k2^{-k} 
$$
when we let $i\to\infty$. On the other hand, $\forall \epsilon > 0$, $\exists i > 0$, $\frac{1}{2^i} < \epsilon$. Thus
$$
\varphi(t_i) > \sum_{k}\frac{1}{2}c_k2^{-k} - \epsilon.
$$ 
So 
$$
\varphi(x) = \sup\{\varphi(t)\mid t\in O\cap[0, x)\} = \frac{1}{2^i}+\sum_{k<i}\frac{1}{2}d_k2^{-k}.
$$
\bigskip
